---
title: "<font size=20>Developing Data Products Week3 <br/> Presentation & Plotly </font>"
author: "Andreia Vieira"
date: "08/07/2020"
output: ioslides_presentation
fontsize: 4pt
encoding: "UTF-8"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
```
## SUMMARY 

###### This activity create a web page using R Markdown and  features a map created with Leaflet. The dataset show the MONITORING PANEL COVID-19 in neighborhoods of Manaus/AM,  in start july Brazil, cases  / 100.000 hab. The dataset  of population of the censo 2010 

##  DATA 

###### COVID-19 Manaus/AM - incidence: cases by 100. 000 hab. in 02 July  2020
<font size ="2"> Fundação de vigilância sanitária – FVS/AM 
Download http://www.fvs.am.gov.br/indicadorSalaSituacao_view/60/2 </font>


###### Population and households - Censo 2010 Manaus/AM
<font size ="2"> IBGE
Download ftp://ftp.ibge.gov.br/Censos/Censo_Demografico_2010/Resultados_do_Universo/Agregados_por_Setores_Censitarios/AM_20171016.zip </font>


```{r, warning=FALSE, message=FALSE}

library(plotly)
library(leaflet)
library(dplyr)
library(htmltools)
library(plotly)
library(knitr)



# Leitura dos dados
covid<-setwd("C:/Mana/ACursoCienciadeDados/Aulas/Desenvolvendo Dados/Projetos")
covid<-read.csv("./COVID19_MANAUS.csv", header=TRUE, sep=";", dec=".")

covid <- covid %>%
dplyr::mutate(grupo = cut(TAXA_COVID, breaks = c(0, 500, 1000, 2000, Inf), labels = c("Abaixo de 500", "Entre 500 e 1000", "Entre 1000 e 2000", "Acima de 2000"))) 

```
## DATASET 
##### COVID19 - MANAUS/AM
```{r, warning=FALSE}
  
   str(covid)

```
## MAP
```{r, warning=FALSE, echo=FALSE, message=FALSE}

p<-plot_ly(data = covid, x = ~NM_BAIRRO, y = ~POPULACAO, type = "scatter", mode = "markers", color=(~grupo))

layout(p,title="COVID19 - MANAUS/AM - 02 /07/2020", xaxis=(list(title="Neighborhoods")), yaxis=(list(title="Population - censo 2010 (*1000)"))) 

```

## CONSIDERATIONS 

- There is no standard with respect to COVID19 indication rate.


